Z-Resonance at LEP

### 2010-07-29 Z0-Publikation/tex/paper-template.tex
hadronen relativ weit

\subsection{Extraction of the cross section}

Example of an equation:

\begin{equation}
\label{a1vm}
A_{1}^{} = \frac{A^{}_{||}}{D^{}}  - \eta \sqrt{R^{}}\ . \\
\end{equation}

@@

\begin{figure}[ht]
\vspace*{-0.2cm}
%\resizebox{0.5\textwidth}{0.35\textwidth}{\includegraphics{./r_06m.eps}}
\caption{\baselineskip=0.38cm Example of a picture}
\label{fig:1}   
\end{figure} 
...

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
energy $\sqrt{s}$ [\si{\GeV}] & myon events & cross section $σ_0^μ$ [\si{\nano\barn}]\\
\hline
89.48 & \phantom{0}67 ± \phantom{0}8 ± \phantom{0}8  & 0.64 ± 0.03 ± 0.3 \\
91.33 & 122 ± 11 ± 10 & 1.53 ± 0.05 ± 0.4 \\
93.02 & \phantom{0}77 ± \phantom{0}9 ± \phantom{0}9 & 0.87 ± 0.04 ± 0.03 \\
\hline
\end{tabular}
\vspace*{0.3cm}
\caption{\baselineskip=0.38cm analyzed hadronic events at different center of mass energies}
\label{tab:myon_events}
\end{center}
\vspace*{-0.5cm}
\end{table}

>>>>

\subsection{Hadronic events}
As it is now known how to extract hadronic events out of the data, it is
possible to determine the hadronic cross section using the following formula:
\begin{equation}
σ_{\mathrm{had}} = \frac{N}{Lε},
\end{equation}
where ε is the efficiency of the cuts. This efficiency could be calculated
using the following equation:
\begin{equation}
ε = \frac{N’_{\mathrm{MC}}}{N_{\mathrm{MC}}},
\end{equation}
where $N’_{\mathrm{MC}}$ is the number of Monte Carlo events that passed the
hadron cuts and $N_{\mathrm{MC}}$ is the total number of events in the Monte
Carlo file.

The hadronic cross section could be calculated at three different center of
mass energies. The number of hadronic events that passed the hadron cuts can be
found in \tref{hadr_events}, as well as the hadronic cross sections themselves.

These cross sections have then been used as data for a fit. By fitting the data
points the overall hadronic cross section, the mass and the hadronic decay width
of the $Z^0$-boson could be determined. The results can be found in
\tref{results}.

@@

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
energy $\sqrt{s}$ [\si{\GeV}] & myon events & cross section $σ_0^μ$ [\si{\nano\barn}]\\
\hline
89.48 & \phantom{0}67 ± \phantom{0}8 ± \phantom{0}8  & 0.64 ± 0.03 ± 0.3 \\
91.33 & 122 ± 11 ± 10 & 1.53 ± 0.05 ± 0.4 \\
93.02 & \phantom{0}77 ± \phantom{0}9 ± \phantom{0}9 & 0.87 ± 0.04 ± 0.03 \\
\hline
\end{tabular}
\vspace*{0.3cm}
\caption{\baselineskip=0.38cm analyzed muonic events at different center of mass
energies}
\label{tab:myon_events}
\end{center}
\vspace*{-0.5cm}
\end{table}
